---
title: "CommunitiesR2"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## CommunitiesR2 package
Helper functions to create network and individual-level metrics relating to igraph's community detection.
```{r setup}
library(CommunitiesR2)
```


### Creating networks
  These functions are designed to create network from dataframes of close contacts (id1, id2 and seconds (or the time of the contact))
```{r}

```

## Community measures
  These include ones related to individual in/out of community strength, and those that contribute to the modularity. 
  
  * Network fragmentation: log number of sub-groups
  * Sub-group cohesion: proportion of contacts that occur within sub-groups
  * Participation coefficient: proportion of contacts made with individuals from the same vs different sub-groups.
  * Zi: a normalised measure of an individuals interactions within its subgroup
  
